---
title: "Week 2 Peer Review"
output: html_document
---

```{r setup, include=FALSE}

######DO NOT MODIFY. This will load required packages and data.

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
cces <- drop_na(read_csv(url("https://www.dropbox.com/s/ahmt12y39unicd2/cces_sample_coursera.csv?raw=1")))
```

Your objective is to replicate these figures, created using the Cooperative Congressional Election Study data. These figures are similar to those we completed in the lecture videos.


## Exercise 1

Hints:

* For the x-axis, use the variable "ideo5".

* Make sure you recode the data for the "ideo5" variable to generate the correct names for the x-axis. You will want to consult the codebook.

* Use the fill aesthetic to have R fill in the bars. You do not need to set the colors manually.

* Use guides() to drop the legend.

* Make sure the axis labels and figure title are correct.


```{r exercise1,echo=FALSE}
####PUT YOUR CODE HERE
cces$ideo5<- recode(cces$ideo5,`1`="Very liberal",`2`="Liberal",`3`="Moderate",`4`="Conservative",`5`="Very conservative")
cces|>
  ggplot(aes(x=ideo5,fill=ideo5)) + geom_bar()+ guides(fill=FALSE) + 
  labs(x="Ideology",y="Count",title="Respondent Ideology")

```

## Exercise 2

Hints:

* For the x-axis, use the variable "pew_religimp".

* Make sure you recode the data for the "pew_religimp" variable to generate the correct labels for the x-axis. You will want to consult the codebook.

* Rename the column for Ideology to make sure the first letter is upper-case (to make the legend appear correctly).

* Use the fill aesthetic to have R fill in the bars. You do not need to set the colors manually.

* Make sure the axis labels and figure title are correct.

```{r exercise2,echo=FALSE}
####PUT YOUR CODE HERE
cces$pew_religimp<-recode(cces$pew_religimp,
                          `1` = "Very important",
                          `2` = "Somewhat important", 
                          `3` = "Not too important",
                          `4` = "Not at all important")
cces|>
  ggplot(aes(x=pew_religimp,fill=ideo5)) + geom_bar() +
  labs(x="Importance of Religion", y="Count", 
       title = "Importance of Religion by Ideology",
       fill="Ideology")
```

## Exercise 3

Instructions:

* For this visualization, you are creating your own data for practice.

* Create a tibble/data frame with three columns: Semester, Student, and Grade.

* There should be six semesters and three students (Amanda, Betty, and Carol)

* Create grades for the students using the runif() command, with values between 80 and 100. Hint: you'll need 18 grades total.

The figure should look approximately like this (your vaules will be slightly different):


```{r exercise3,echo=FALSE}
####PUT YOUR CODE HERE
my_dat <- 
  tibble("Semester" = 1:6 %>% rep(times = 3),
         "Student" = c("Amanda", "Betty", "Carol") %>% rep(each=6),
         "Grade" = runif(18,80,100)
)
my_dat|>
  ggplot(aes(x=Semester,y=Grade,color=Student)) + facet_wrap(~Student) + geom_line() + theme(legend.position = "none")
```
